---
title: "1020_datawranglingII_m4"
author: "Yutian Luo"
date: "10/21/2020"
output: 
  html_document:
    toc: true
    float_toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(rvest)
library(httr)
```


# Part I: reading data from web

## 1. read web to df
1. read_html()
2. html_nodes(css = )

```{r read web df}
url_drug = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"    # define url

drug_use_html = read_html(url_drug)   # define html, read url 

drug_use_html %>%                    # select table from readed html
  html_nodes(css = "table")

```



## 2. df table manipulation

1. first(),    select first table
2. html_table()     convert to df
3. slice()   remove 1st row
4. as_tibble()    convert to tibble, easy to view

```{r read table}
table_marj = 
  drug_use_html %>% 
  html_nodes(css = "table") %>%     # select table
  first() %>%            # select first table from web
  html_table() %>%       # convert to df
  slice(-1) %>%          # remove 1st row
  as_tibble()
  
view(table_marj)
```



### learning assess
Create a data frame that contains the cost of living table for New York from this page

1. html_nodes().[[i]]    start from row i

```{r read from website table}
nyc_living = 
  read_html("https://www.bestplaces.net/cost_of_living/city/new_york/new_york") %>% 
  html_nodes(css = "table") %>% 
  .[[1]] %>%       # start from the 1st row
  html_table(header = TRUE)
  
nyc_living
```



## 3. CSS selector

1. html_nodes(css = "...")
2. html_text        grab text

```{r}
star_war_titles = 
  read_html("https://www.imdb.com/list/ls070150896/") %>% 
  html_nodes(css = ".lister-item-header a") %>% 
  html_text()

star_war_groos = 
  read_html("https://www.imdb.com/list/ls070150896/") %>% 
  html_nodes(css = ".text-muted .ghost~ .text-muted+ span") %>% 
  html_text()

run_time = 
  read_html("https://www.imdb.com/list/ls070150896/") %>% 
  html_nodes(css = ".runtime") %>% 
  html_text()

# comibine into one df
star_war_df = 
  tibble(
    name = star_war_titles,
    gross_rev = star_war_groos,
    run_time = run_time
  )
```


learning assesment

scrape data from "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_getr_d_paging_btm_prev_1?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1", get most recent review's titles

```{r}
napolean_url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_getr_d_paging_btm_prev_1?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

napolean = read_html(napolean_url)

napolean_title = 
  napolean %>% 
  html_nodes(css = ".a-text-bold span") %>% 
  html_text()

napolean_rating = 
  napolean %>% 
  html_nodes(css = "#cm_cr-review_list .review-rating") %>% 
  html_text()

napolean_text = 
  napolean %>% 
  html_nodes(css = ".review-text-content span") %>% 
  html_text()

napolean_df = 
  tibble(
    titles = napolean_title,
    rating = napolean_rating,
    texts = napolean_text
  )

knitr::kable(napolean_df)
```



## API && web scraping data

1. get()
2.content()
3. jsonlite::fromJSON()

```{r}
# from csv
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.csv") %>% 
  content("parsed")

# from json
nyc_water = 
  GET("https://data.cityofnewyork.us/resource/ia2d-e54m.json") %>% 
  content("text") %>% 
  jsonlite::fromJSON() %>% 
  as_tibble()
```


### cdc RFSS example

1. API limitations: ie, default query rows
2. read API Docs and R docs to solve issues

```{r}
cdc_2010 = 
  GET("https://chronicdata.cdc.gov/resource/acme-vg9e.csv", 
      query = list("$limit" = 50000)) %>% 
  content("parsed")
```


# miscellaneous web data

```{r}
pokiemon = 
  GET("https://pokeapi.co/api/v2/pokemon/1") %>% 
  content

pokiemon$weight
pokiemon$height

```







